Robust Winner Determination and Simultaneous Elicitation of Scoring Rule and Agents Preferences

### 2020-01-15 draft.tex
title and abstract

\title{Robust Winner Determination and Simultaneous Elicitation of Scoring Rules and Preferences}

@@

In this setting, we propose a method  for robust approximate winner determination with minimax regret. 
Moreover, we provide an interactive elicitation protocol based on minimax regret
and develop several query strategies that interleave questions to the chair and questions to the agents in order to attempt to acquire the most relevant information in order to quickly converge to optimal or a near-optimal alternative.
\end{abstract}

@@

% In the code, called Current solution
We also define the \strat{Extreme completions} strategy, which we consider as a more realistic baseline. 
Consider the solution of the minimax regret game, 
 $(x^{*},\bar{y},\bar{\profile},\bar{\w})$, where $x^{*}$ is the minimax regret optimal alternative, and $\bar{y} = \arg \max_{y \in A} \PMR(x,y; \pprofile, W)$, $\bar{\profile}$ and $\bar{\w}$ are the adversarial choices, thus, the instantiations that, given the choice of $x^*$, maximize the regret. 
Define: 
\begin{align}
\tau_{1} & = \min_{\w \in W} s(\bar{y}; \bar{\profile}, \w) - s(x^{*}; \bar{\profile}, \w),  \label{eq:tau1} \\
\tau_{2} & = \min_{\profile \in C(\pprofile)} s(\bar{y},\profile, \bar{\w}) -  s(x^{*}; \profile, \bar{\w}).
\end{align}
{\color{red}
\begin{align}
	\tau_{wg} & = \min_{\w \in W} s^{\bar{\profile},\w}(\bar{y}) - s^{\bar{\profile},\w}(x^{*}) \\
	\tau_{i} & = \min_{\profile_i \in C(\pprofile)} s^{(\bar{\profile}_{-i},\profile_i),\bar{\w}}(\bar{y}) -  s^{(\bar{\profile}_{-i},\profile_i),\bar{\w}}(x^{*}) 
\end{align}
or we can use $\hat{\profile_i}=(\bar{\profile}_{-i},\profile_i)$ which is defined as $\bar{\profile}$ except for $i$, $\forall i \in \{1, \dots, n\}$. }

>>>>

\title{Robust Winner Determination and Simultaneous Elicitation of Scoring Rule and Agents Preferences}

@@

In this setting, we propose a method  for robust approximate winner determination with minimax regret. 
We also provide an interactive elicitation protocol based on minimax regret
and develop several query strategies that interleave questions to the chair and questions to the agents in order to attempt to acquire the most relevant information in order to quickly converge to optimal or a near-optimal alternative.
\end{abstract}

@@

% In the code, called Current solution
We also define the \strat{Extreme completions} strategy, which we consider as a more realistic baseline. 
Consider the solution of the minimax regret game, 
 $(x^{*},\bar{y},\bar{\profile},\bar{\w})$, where $x^{*}$ is the minimax regret optimal alternative, and $\bar{y} = \arg \max_{y \in A} \PMR(x,y; \pprofile, W)$, $\bar{\profile}$ and $\bar{\w}$ are the adversarial choices, thus, the instantiations that, given the choice of $x^*$, maximize the regret. 
Define: 
\begin{align}
\tau_{1} & = \min_{\w \in W} s(\bar{y}; \bar{\profile}, \w) - s(x^{*}; \bar{\profile}, \w),  \label{eq:tau1} \\
\tau_{2} & = \min_{\profile \in C(\pprofile)} s(\bar{y},\profile, \bar{\w}) -  s(x^{*}; \profile, \bar{\w}).
\end{align}
{\color{red}
\begin{align}
	\tau_{\text{wgt}} & = \min_{\w \in W} s^{\bar{\profile},\w}(\bar{y}) - s^{\bar{\profile},\w}(x^{*}) \\
	\tau_{i} & = \min_{\profile_i \in C(\pprofile)} s^{(\bar{\profile}_{-i},\profile_i),\bar{\w}}(\bar{y}) -  s^{(\bar{\profile}_{-i},\profile_i),\bar{\w}}(x^{*}) 
\end{align}
or we can use $\hat{\profile_i}=(\bar{\profile}_{-i},\profile_i)$ which is defined as $\bar{\profile}$ except for $i$, $\forall i \in \{1, \dots, n\}$. }
